Compare pseqs

### 2019-05-27 comparepseqs.Rmd
Print subset

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
library(ggpubr)
```

@@

```{r subset runs}
if (exists("subset.run")) {
    message(paste0("Subset ", subset.run))
    rds <- rds[subset.run]
}

@@

for (key in names(rds)) {
    alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alpha-", key , ".rds"))

    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])
diversities$min
    alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.6)
    alpha.diversity.full <- plot.alpha(diversities$full, colorlimit = 0.6)

@@

```{r debug, eval = FALSE}
ret[["centrifuge"]]$betadiversity$full$model_1
```

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
library(ggpubr)
library(broom)
library(tidyr)
```

@@

```{r subset runs}
if (exists("subset.run")) {
    message(sprintf("Subset %s of %s", subset.run, rds[[subset.run]]))
    rds <- rds[subset.run]
}

@@

for (key in names(rds)) {
    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])

    alpha.diversity.min <- plot.alpha(diversities$min, alphabreaks = c(-0.15, -0.10, -0.05, 0))
    alpha.diversity.full <- plot.alpha(diversities$full, alphabreaks = c(-0.15, -0.10, -0.05, -0))

@@

```{r debug, eval = FALSE}
alphalist <- c()
for (key in names(rds)) {
    alphalist <- c(alphalist,
              ret[[key]]$alphadiversity$min %>% pull(estimate),
              ret[[key]]$alphadiversity$full %>% pull(estimate))
}

summary(alphalist)
```

```{r alpha size, eval = FALSE}
pseq <- import_filter_data(rds[["gtdb"]])

dset <- meta.merge.alphadiversity(pseq) %>%
    mutate(diversities_shannon = scale(diversities_shannon))

dset %>%
    select(MAP, diversities_shannon) %>%
    gather(key, value) %>%
    group_by(key) %>%
    summarise_all(funs(N = n(),
                       min = min(as.numeric(value), na.rm = TRUE),
                       max = max(as.numeric(value), na.rm = TRUE),
                       Mean = mean(as.numeric(value), na.rm = TRUE),
                       SD = sd(as.numeric(value), na.rm = TRUE),
                       NAs = sum(is.na(value))))  %>%
    kable()

lm(sprintf(fo.alpha.full, "SYSTM"), data = dset) %>% summary
```

```{r size}
Reduce(function(...) merge(..., all=T), ret)
```
